This module encapsulate all the knowledge needed by the agent to make decisions. This module is divided in specialized sub-modules, which are in charge to have the information specific information and make inference from these. These sub-modules are:
\begin{itemize}
	\item \textit{Sensory information and processing}: sense the robot's environment. Depending of the capabilities of the robotic platform, this module could capture meaningful information.
	\item \textit{World model}: is the representation of the surround environment.
	\item \textit{Social world model}: infers the current situation, and it has a the possible emotional state of the other people that are present.
	\item \textit{Rational social model}: has the relation of the character with other people and roles.
	\item \textit{Emotional model}: infers the emotional state based on the information coming from the social world model and rational social model.
	\item \textit{Delegated goals}: are those responsibilities that the agent have to follow. This is given by the character. 
\end{itemize}
\subsection{The delegated goals}
The delegated goals are an important component in the coordination because \todo[inline]{write why is important this in the coordination context}. This information is encapsulated in the script, and it gives \todo[inline]{write precisely which information gives this module}.\\ 
The structure of one goal is define as follows:
\begin{itemize}
\item The pre-condition: indicates the facts that must be true for consider the goal as a potential goal to become a desire. \todo[inline]{write about what is a fact and how is recognized}

\item The post-condition: is the desire state of the world, it means those facts that the agent want to be true. \todo[inline]{a little example}

\item The plan of action: is a predefined graph of simple actions that trace the path the agent have to follow in order to reach the goal's post-condition. With the graph representation the actions could be executed in parallel. \todo[inline]{to general, give an concrete description of these.}
\end{itemize}
This structure of the goal also applies to the desires and intention, which are goals in different stages of the deliberative process. 
